Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-19 rates-neurips-21/rates.tex
fix compile error
intro pass on rates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Machine learning is important.

Mention that the techniques focus on the ``conditional problem''.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\paragraph{The surrogate risk framework.}
In supervised learning, data is of the form $(x,y)$ and the goal is to learn a hypothesis $g(x)$.
This paper considers the common setting where the space of labels $y$ is finite, as is the space of predictions $g(x)$, and accuracy is measured with a \emph{target loss function} $\ell(g(x),y)$.

Because these discrete settings are generally computationally challenging, a common paradigm is to learn $g$ via \emph{surrogate risk minimization}:
\begin{enumerate}
  \item Define a \emph{surrogate loss function} $L(h(x),y)$ over a more-tractable continuous, convex prediction space.
  \item Learn a hypothesis $h(x)$ mapping $x$ to this new prediction space.
  \item Produce a hypothesis $g(x)$ for the original, target problem using some link function $\psi$ via $g(x) = \psi(h(x))$.
\end{enumerate}
For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
Common surrogate losses include hinge loss and logistic loss.
These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.

\paragraph{Rates of convergence.}
Given $n$ data points and a surrogate loss $L$, a learning algorithm should produce a hypothesis $h_n$ whose loss converges to the optimal possible as $n$ increases.
Specifically, we can define $\mathrm{Regret}_{L}(h)$ as the expected loss of $h$ on the data distribution, minus the expected loss of the Bayes optimal predictor, i.e. the measurable function with least loss.
Then a primary goal is to bound the \emph{convergence rate} of this algorithm, i.e. provide a bound of the form $\mathrm{Regret}_{L}(h_n) \leq O\left(\tfrac{1}{n^{\alpha}}\right)$.
Such bounds for $\alpha = \tfrac{1}{2}$ are considered ``slow'' rates and are guaranteed by e.g. VC-dimension bounds.\bo{cite}
Faster rates such as $\alpha = 1$ are obtainable is some settings.\bo{cite}

\paragraph{Problem: relating surrogate and target regret.}
However, results of the above form do not guarantee the success of the learning framework for the original, target problem.
Even if the surrogate regret $\mathrm{Regret}_L(h_n)$ is small, we actually care about the induced target hypothesis $g_n = \psi \circ h_n$.
Will the target regret necessarily be small?
Motivated by this problem, this paper will study \emph{surrogate regret bounds}.\bo{cite}
%A surrogate regret bound answers the following question: when we minimize the \emph{surrogate} regret at a given rate, how fast does the \emph{target} regret diminish?
Informally, a surrogate regret bound takes the form
\begin{equation}
  \label{eq:surrogate-regret-bound-informal}
  \forall \text{ hypotheses } h:\X\to\reals^d, \quad \mathrm{Regret}_\ell(\psi\circ h) \leq \zeta(\, \mathrm{Regret}_L(h) \,)~,
\end{equation}
where the regret transfer function $\zeta : \reals_+ \to \reals_+$ controls how surrogate regret translates to target regret.
For example, \bo{cite} studies the \bo{??} surrogate loss for the \bo{??} problem, achieving a guarantee of $\zeta(\epsilon) \leq O\left(\sqrt{\epsilon}\right)$.

While such a guarantee is certainly nice, it is not ideal: even if one achieves a fast rate of $O(\tfrac{1}{n})$ for the surrogate problem, this only translates to the slow rate guarantee of $O(\tfrac{1}{n^{1/2}})$ in the target problem that we actually want to solve.
Preferable would be a transfer function such as $\zeta(\epsilon) = O(\epsilon^{3/4})$ or even $\zeta(\epsilon) = O(\epsilon)$, a linear transfer rate.

\raf{Of particular interest is the concavity of $\zeta$} \bo{explain why?}

By considering a specific class of surrogate losses -- \emph{polyhedral}, generalizations of piecwise-linear convex -- we will show that this utopia is in fact achieved for every surrogate in this class.

%\begin{theorem}[Linear bounds for polyhedral surrogates]
\begin{theorem}[Main surrogate regret bound]
  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
\end{theorem}

We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
\begin{theorem}[Main lower bound]
  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}

\bo{example/discussion?}

\paragraph{Other related work.}
\bo{Any?}
